### 2019-01-21 macro3_1.tex
Macro

	\item Of course in general the answer to this question depends on the particular type of function $u()$, however if we assume "good" increasing and concave utility function then price of marginal piece of cake increases over time. From the Euler's equation (which is obtained in 5.) $\frac{u'(c(t))}{u'(c(t+1))} = \frac{\lambda(t)}{\lambda(t+1)} = \beta$. Since $\lambda(t) = V'(k(t))$ then $\frac{V'(k(t))}{V'(k(t+1))} = \beta < 1$. That means that $V'(k(t))$ is increasing over time. Since $\rho$ is a constant (its meaning is the interest rate) then to hold it constant with increasing denumerator, the numerator $V'(k(t+1)) - V'(k(t))$ should also increase but $V'(k(t+1)) - V'(k(t))$ is exactly the price of marginal piece of cake. Intuitivelly it can be understood as follows: the amount of capital is shrinking hence over time the agent values each marginal unit of capital more and more. 
	\item Using the same equations as in the 2. $\frac{V'(k(t))}{V'(k(t+1))} = \beta$, that means that the present value of the whole cake stay constant: \begin{align*}

@@

	In the same time the current value is increasing, which can be inferred from $\frac{V'(k(t))}{V'(k(t+1))} = \beta < 1$.
	\item Present value is constant, current is increasing with rate $\frac{1}{\beta}$.

@@

that means that in this case even present value will increase over time:

@@

Applying shouting algoritm the following value of $k(2)$ has been obtained:
\begin{align*}
k(2) = 0.1368665097187844
\end{align*}
and corresponding capital and consumption paths are depicted on the Fig. \ref{fig1} , \ref{fig2} respectively.
\begin{figure}[h]
	\centering
	\includegraphics[width=0.8\textwidth]{k(t)}
	\caption{}\label{fig1}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.8\textwidth]{c(t)}
	\caption{}\label{fig2}
\end{figure}

>>>>

	\item Of course in general the answer to this question depends on the particular type of function $u()$, however if we assume "good" increasing and concave utility function then price of marginal piece of cake increases over time. It can be inferred both from the asset pricing equation and from the Euler's equation. From the asset pricing equation it is obviously that LHS is nonnegative (its meaning is the interest rate) hence the RHS should be also nonnegative. The denominator of the LHS is nonnegative because economically it is a shadow price of capital or matimatically it is equal to corresponding lagrange multiplier which cannot be negative by the Kuhn and Tucker theorem. Thus, numerator should be also nonnegative, so $V'(k(t+1)) \ge V'(k(t))$ i.e. price of marginal piece of cake increases over time. From the Euler's equation (which is obtained in 5.) $\frac{u'(c(t))}{u'(c(t+1))} = \frac{\lambda(t)}{\lambda(t+1)} = \beta$. Since $\lambda(t) = V'(k(t))$ then $\frac{V'(k(t))}{V'(k(t+1))} = \beta < 1$. That means that $V'(k(t))$ is increasing over time. Intuitivelly it can be understood as follows: the amount of capital is shrinking hence over time the agent values each marginal unit of capital more and more. 
	\item Under some assumptions on the utility function it can be proved that $V(k)$ is strictly increasing. In our problem $k$ is decreasing over time that means that $V(k)$ should also decrease over time, i.e. the value of the whole cake decreases.
	\item Using the same equations as in 2. $\frac{V'(k(t))}{V'(k(t+1))} = \beta$, that means that the present value of the marginal piece of cake remains constant: \begin{align*}

@@

	At the same time the current value is increasing, which can be inferred from $\frac{V'(k(t))}{V'(k(t+1))} = \beta < 1$.

@@

that means that in this case even present value of marginal piece of cake will increase over time:

@@

Applying shouting algoritm the following value of $k(2)$ has been obtained:
\begin{align*}
k(2) = 0.1368665097187844
\end{align*}
and corresponding capital and consumption paths are depicted on the Fig. \ref{fig1} , \ref{fig2} respectively.
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{k(t)}
	\caption{}\label{fig1}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.8\textwidth]{c(t)}
	\caption{}\label{fig2}
\end{figure}
